---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DoubleCauchy

<!-- badges: start -->
<!-- badges: end -->

The goal of DoubleCauchy is to provide a stable and adaptive test for 
simultaneously testing regression coefficients of 
generalized linear models of high dimensional data.
The flexible framework proposed can be directly applied 
to leverage side information for polygenic signal detection.

## Installation

You can install the released version of DoubleCauchy with:

``` r
devtools::install_github("yanyan-zhao/DoubleCauchy")
```

## Example

```{r example}
library(DoubleCauchy)
## basic example code
```

Example 1: "AdapSide" function to leverage side information.

```{r AdapSide}
 J = 100
 n = 50
 beta=c(rep(2,3),rep(0,J-3))
 data=example_data_generate(n, J, beta)
 Y=data$Y
 G=data$G
 lam=0.1
 weights=c(J:1)
 pow.param=c(1:5)
 AdapSide(Y, G, cor.est="pdsoft", lam, weights, pow.param)
```

Example 2: A stable and adaptive test based on repeated sample splitting

```{r DCSIS, echo = T}
 J = 100
 n = 50
 beta=c(rep(2,3),rep(0,J-3))
 data=example_data_generate(n, J, beta)
 Y=data$Y
 G=data$G
 lam=0.1
 weights=c(J:1)
 pow.param=c(1:5)
 n1=20
 m=10
 DoubleCauchy(n1, m, Y, G, varselec.method="DCSIS", J2=10, cor.est="pdsoft", lam=lam, pow.param=pow.param)

```

## Reference

Zhao and Sun (2020). A stable and adaptive polygenic signal detection method based on repeated sample splitting.

